---
title: "Additional_variable_stats"
author: "Serena Verdi"
date: "26/10/2021"
output: html_document
---

Summary: This script runs statistical tests on cleaned cognitive, biospecimen (CSF amyloid and p-tau) and apoe genotype data. Data has been cleaned and processed via the 'Additional_varaibles_SV' script, this will need to be run, and outputs will need to be saved before running this script

Paths to data will need to be changed accordingly.


#-----------------------------------------------
# Code setup
#-----------------------------------------------
# Librarys
```{r setup}
library(dplyr)
library(psych)
library(tidyr)
library(readr)
library(ADNIMERGE)
library(data.table)
library(matrixStats)
library(cowplot)
library(extrafont)
```

# Clear workspace
```{r}
rm(list = ls())
```
#Read in data 

```{r}
## Composite Cognitive Score
z_cc <- read.csv("~/OneDrive - University College London/Chapter 2 cross sectional AD/ADNI_project/Full_study/Results/z_score_stats_cognition/z_scores_cc.csv")

## CSF measures
z_csf <- read.csv("~/OneDrive - University College London/Chapter 2 cross sectional AD/ADNI_project/Full_study/Results/z_score_biospec/z_scores_bs.csv")

## MMSE Updated!
z_mmse <- read.csv("~/OneDrive - University College London/Chapter 2 cross sectional AD/ADNI_project/Full_study/Results/z_score_stats_cognition/z_score_mmse_updated.csv")  


## APOE status

z_apoe <- read.csv("~/OneDrive - University College London/Chapter 2 cross sectional AD/ADNI_project/Full_study/Results/z_score_biospec/z_scores_apoe.csv")
```
#Column names
```{r}
#colnames(z_cc)
```
#-----------------------------------------------
#Create total outlier score
#-----------------------------------------------
# Thresholding z-scores 
```{r}
# outlier_threshold <- -1.65 ## bottom 5%
outlier_threshold <- -1.96 ## bottom 2.5%
# outlier_threshold <- -2.58 ## bottom 0.05%
```
# Binerising z-scores
```{r}
# z-cc
temp<- as.data.frame(ifelse(z_cc[,7:155] < outlier_threshold,1,0))
temp <- temp %>% rename_all(paste0, "_bin")
z_cc$total_outlier_score <- rowSums(temp)
z_cc <- cbind(z_cc, temp)

#z-csf
temp<- as.data.frame(ifelse(z_csf[,7:155] < outlier_threshold,1,0))
temp <- temp %>% rename_all(paste0, "_bin")
z_csf$total_outlier_score <- rowSums(temp)
z_csf <- cbind(z_csf, temp)

#z-mmse
temp<- as.data.frame(ifelse(z_mmse[,33:181] < outlier_threshold,1,0))
temp <- temp %>% rename_all(paste0, "_bin")
z_mmse$total_outlier_score <- rowSums(temp)
z_mmse <- cbind(z_mmse, temp)


#z-apoe
temp<- as.data.frame(ifelse(z_apoe[,7:155] < outlier_threshold,1,0))
temp <- temp %>% rename_all(paste0, "_bin")
z_apoe$total_outlier_score <- rowSums(temp)
z_apoe <- cbind(z_apoe, temp)
```
# Create seperate datasets with group
```{r}
#z_cc
z_cc_controls <- z_cc[grep("Controls", z_cc$diagnosis.x), ] 
z_cc_mci <- z_cc[grep("MCI", z_cc$diagnosis.x), ] 
z_cc_dementia <- z_cc[grep("Dementia", z_cc$diagnosis.x), ] 

#z_csf
z_csf_controls <- z_csf[grep("Controls", z_csf$diagnosis.x), ] 
z_csf_mci <- z_csf[grep("MCI", z_csf$diagnosis.x), ] 
z_csf_dementia <- z_csf[grep("Dementia", z_csf$diagnosis.x), ] 


#z_mmse
z_mmse_controls <- z_mmse[grep("CN", z_mmse$diagnosis.x), ] 
z_mmse_mci <- z_mmse[grep("MCI", z_mmse$diagnosis.x), ] 
z_mmse_dementia <- z_mmse[grep("Dementia", z_mmse$diagnosis.x), ] 
```
# Overall group interaction of total outlier score
```{r}
z_cc$diagnosis.x <-  as.factor(z_cc$diagnosis.x)
summary(lm(total_outlier_score ~ diagnosis.x, data = z_cc))
```


#-----------------------------------------------
# Linear regression on composite cognitive scores
#-----------------------------------------------
# Memory

```{r}
## Main effect
#summary(lm(ADNI_MEM ~ total_outlier_score, data = z_cc)) 
#s1<- lm(ADNI_MEM ~ total_outlier_score, data = z_cc)
#confint(s1) ##gives CI

##interaction
summary(lm(ADNI_MEM ~ total_outlier_score*diagnosis.x + age + gender, data = z_cc)) ##outcome ~ predictor
anova(lm(ADNI_MEM ~ total_outlier_score*diagnosis.x + age + gender, data = z_cc))
#summary(lm(ADNI_MEM ~ total_outlier_score + diagnosis.x + age + gender + total_outlier_score:diagnosis.x, data = z_cc)) ##outcome ~ predictor

## main effect adjusted 
summary(lm(ADNI_MEM ~ total_outlier_score + diagnosis.x + age + gender, data = z_cc)) ##outcome ~ predictor main effect
```
# Executive function
```{r}
## main effect
#summary(lm(ADNI_EF ~ total_outlier_score, data = z_cc)) 

## interaction
##interaction
summary(lm(ADNI_EF ~ total_outlier_score*diagnosis.x + age + gender, data = z_cc)) ##outcome ~ predictor
anova(lm(ADNI_EF ~ total_outlier_score*diagnosis.x + age + gender, data = z_cc))
#summary(lm(ADNI_MEM ~ total_outlier_score + diagnosis.x + age + gender + total_outlier_score:diagnosis.x, data = z_cc)) ##outcome ~ predictor

## main effect adjusted 
summary(lm(ADNI_EF ~ total_outlier_score + diagnosis.x + age + gender, data = z_cc)) ##outcome ~ predictor main effect
```
#-----------------------------------------------
# Visualisations
#-----------------------------------------------
# change dementia to AD in diagnosis
```{r}
z_cc$diagnosis.x <- gsub("Dementia", "AD", z_cc$diagnosis.x)

```

# change order of factors to suit figure legend
```{r}
z_cc$diagnosis.x <- factor(z_cc$diagnosis.x, levels = c("Controls", "MCI", "AD"))

```

# total_outlier_score x ADNI_MEM
```{r}
# loess real fit (local estimate of smoothing)
ggplot(z_cc, aes(x = total_outlier_score , y = ADNI_MEM )) + 
  geom_point() +
  stat_smooth(method = "loess", col = "red" , size = 1)

# quadratic
ggplot(z_cc, aes(x = total_outlier_score, y = ADNI_MEM, color= diagnosis.x )) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x + I(x^2), size = 1)

# lines for each group
p <- z_cc %>% ggplot(aes(total_outlier_score, ADNI_MEM)) 
p + 
  geom_point(aes(col = diagnosis.x)) + 
    geom_smooth(aes(col = diagnosis.x), method = 'lm', formula = y ~ x + I(x^2)) +
    theme(legend.background = element_rect(fill = "transparent"),
          legend.justification = c(0, 1),
          legend.position = c(0, 1))


# lines for each group
p <- z_cc %>% ggplot(aes(total_outlier_score, ADNI_MEM)) 
p + 
  # geom_point(aes(col = diagnosis.x)) + 
    # geom_smooth(aes(col = diagnosis.x), method = 'lm', formula = y ~ x + I(x^2)) +
    geom_smooth(aes(col = diagnosis.x), method = 'lm', formula = y ~ x) +
  geom_smooth(method = 'lm', formula = y ~ x, col = "black") +
    theme(legend.background = element_rect(fill = "transparent"),
          legend.justification = c(0, 1),
          legend.position = c(0, 1))


# lines for each group
p <- z_cc %>% ggplot(aes(total_outlier_score,ADNI_MEM)) 
p + 
  geom_smooth(aes(col = diagnosis.x), method = 'lm', formula = y ~ x, fill= "snow2") +
  theme_minimal() +
  theme(text=element_text(family="Times New Roman", face="bold", size=16)) + #Times New Roman, 12pt, Bold
  labs(colour = "Group", y= "Memory function", x= "Total outlier score") + # change label text
  scale_color_manual(values=c("Controls" =  "grey65" ,  "MCI" ="mediumturquoise", "AD"="lightslateblue"))

```

# total_outlier_score x ADNI_EF
```{r}
# linear
ggplot(z_cc, aes(x = total_outlier_score , y = ADNI_EF )) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x , size = 1)


# quadratic
ggplot(z_cc, aes(x = total_outlier_score, y = ADNI_EF, color= diagnosis.x)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x + I(x^2), size = 1)

# lines for each group
p <- z_cc %>% ggplot(aes(total_outlier_score, ADNI_EF)) 
p + 
  geom_point(aes(col = diagnosis.x)) + 
    geom_smooth(aes(col = diagnosis.x), method = 'lm', formula = y ~ x + I(x^2)) +
    theme(legend.background = element_rect(fill = "transparent"),
          legend.justification = c(0, 1),
          legend.position = c(0, 1))


# lines for each group
p <- z_cc %>% ggplot(aes(total_outlier_score, ADNI_EF)) 
p + 
  geom_smooth(aes(col = diagnosis.x), method = 'lm', formula = y ~ x, fill= "snow2") +
  theme_minimal() +
  theme(text=element_text(family="Times New Roman", face="bold", size=16)) + #Times New Roman, 12pt, Bold
  labs(colour = "Group", y= "Executive function", x= "Total outlier score") + # change label text
  scale_color_manual(values=c("Controls" =  "grey65" ,  "MCI" ="mediumturquoise", "AD"="lightslateblue"))
```
#-
# R_G_precentral (primary somatosensory cortex)  x ADNI_MEM
```{r}
#Raw z-scores 

summary(lm(ADNI_MEM ~ R_G_precentral + age + gender, data = z_cc))

ggplot(z_cc, aes(x = R_G_precentral , y = ADNI_MEM, color= diagnosis.x)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x , size = 1)


# line though groups

z_cc$diagnosis.x <- as.factor(z_cc$diagnosis.x)
is.factor(z_cc$diagnosis.x)

p <- z_cc %>% ggplot(aes(R_G_precentral, ADNI_MEM)) 

p + 
  geom_point(aes(col = diagnosis.x)) + 
    geom_smooth(aes(col = diagnosis.x), method = 'lm') +
    theme(legend.background = element_rect(fill = "transparent"),
          legend.justification = c(0, 1),
          legend.position = c(0, 1))

```
# L_S_postcentral (primary motor cortex) x ADNI_MEM
```{r}
#Raw z-scores 

summary(lm(ADNI_MEM ~ L_S_postcentral*diagnosis.x + age + gender, data = z_cc))

ggplot(z_cc, aes(x = L_S_postcentral , y = ADNI_MEM, color= diagnosis.x)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x , size = 1)


# line though groups

z_cc$diagnosis.x <- as.factor(z_cc$diagnosis.x)
is.factor(z_cc$diagnosis.x)

p <- z_cc %>% ggplot(aes(L_S_postcentral, ADNI_MEM)) 

p + 
  geom_point(aes(col = diagnosis.x)) + 
    geom_smooth(aes(col = diagnosis.x), method = 'lm') +
    theme(legend.background = element_rect(fill = "transparent"),
          legend.justification = c(0, 1),
          legend.position = c(0, 1))

```

# hippocampus x ADNI_MEM
```{r}
#Raw z-scores 

summary(lm(ADNI_MEM ~ L_G_oc.temp_med.Parahip + age + gender, data = z_cc))

ggplot(z_cc, aes(x = L_G_oc.temp_med.Parahip , y = ADNI_MEM, color= diagnosis.x)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x , size = 1)


# line though groups

z_cc$diagnosis.x <- as.factor(z_cc$diagnosis.x)
is.factor(z_cc$diagnosis.x)

p <- z_cc %>% ggplot(aes(L_G_oc.temp_med.Parahip, ADNI_MEM)) 

p + 
  geom_point(aes(col = diagnosis.x)) + 
    geom_smooth(aes(col = diagnosis.x), method = 'lm') +
    theme(legend.background = element_rect(fill = "transparent"),
          legend.justification = c(0, 1),
          legend.position = c(0, 1))

```
# Decriptives
```{r paged.print=FALSE}
describeBy(z_csf$ABETA, z_csf$diagnosis.x, IQR = T)
describeBy(z_csf$PTAU, z_csf$diagnosis.x, IQR = T)

mean(z_csf$ABETA)
sd(z_csf$ABETA)

mean(z_csf$PTAU)
sd(z_csf$PTAU)



```
#-----------------------------------------------
# Linear regression on CSF measures
#-----------------------------------------------
# ABETA
```{r}
#unadjusted INTERACTIONS
#summary(lm(total_outlier_score ~ ABETA*diagnosis.x, data = z_csf))
anova(lm(total_outlier_score ~ ABETA*diagnosis.x, data = z_csf))
#summary(lm(total_outlier_score ~ ABETA + diagnosis.x  + ABETA:diagnosis.x, data = z_csf)) #same as above

#unadjusted MAIN EFFECT
summary(lm(total_outlier_score ~ ABETA, data = z_csf))
#anova(lm(total_outlier_score ~ ABETA, data = z_csf))
# adjusted for hippocampal volume
#summary(lm(total_outlier_score ~ ABETA + hemimean_hippcampal_vol , data = z_csf)) 
```

# PTAU
```{r}
#unadjusted INTERACTIONS
#summary(lm(total_outlier_score ~ PTAU*diagnosis.x, data = z_csf))
anova(lm(total_outlier_score ~ PTAU*diagnosis.x, data = z_csf))
#summary(lm(total_outlier_score ~ PTAU + diagnosis.x  + PTAU:diagnosis.x, data = z_csf)) #same as above

#unadjusted MAIN EFFECT
summary(lm(total_outlier_score ~ PTAU, data = z_csf))

#unadjusted ##interactions only
#summary(lm(total_outlier_score ~ PTAU:diagnosis.x, data = z_csf))
```
#-----------------------------------------------
# Visualisations
#-----------------------------------------------

# change dementia to AD in diagnosis
```{r}
z_csf$diagnosis.x <- gsub("Dementia", "AD", z_csf$diagnosis.x)

```

# change order of factors to suit figure legend
```{r}
z_csf$diagnosis.x <- factor(z_csf$diagnosis.x, levels = c("Controls", "MCI", "AD"))

```
# total_outlier_score x ABETA
```{r}
# linear
ggplot(z_csf, aes(x = ABETA , y = total_outlier_score, color= diagnosis.x )) + 
  geom_point() +
  xlim(90, 300) +
  ylim(2, 80) +
  stat_smooth(method = "lm", col = "red", formula = y ~ x , size = 1)

# quadratic
ggplot(z_csf, aes(x = ABETA, y = total_outlier_score, color= diagnosis.x )) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x + I(x^2), size = 1)

#log transform ABETA
ggplot(z_csf, aes(x = ABETAlog , y =total_outlier_score, color= diagnosis.x)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x , size = 1)

# lines for each group
p <- z_csf %>% ggplot(aes(ABETAlog, total_outlier_score)) 
p + 
  geom_point(aes(col = diagnosis.x)) + 
    geom_smooth(aes(col = diagnosis.x), method = 'lm') +
    theme(legend.background = element_rect(fill = "transparent"),
          legend.justification = c(0, 1),
          legend.position = c(0, 1))

# lines for each group
p <- z_csf %>% ggplot(aes(ABETAlog, total_outlier_score)) 
p + 
  geom_smooth(aes(col = diagnosis.x), method = 'lm', formula = y ~ x, fill= "snow2") +
  theme_minimal() +
  theme(text=element_text(family="Times New Roman", face="bold", size=12)) + #Times New Roman, 12pt, Bold
  labs(colour = "Group", y= "Total outlier score", x= "CSF amyloid") + # change label text
  scale_color_manual(values=c("Controls" =  "grey65" ,  "MCI" ="mediumturquoise", "AD"="lightslateblue"))


# lines for each group
p <- z_csf %>% ggplot(aes(ABETAlog, total_outlier_score)) 
p + 
  geom_smooth(aes(col = diagnosis.x), method = 'lm', formula = y ~ x, fill= "snow2") +
  theme_minimal() +
  theme(text=element_text(family="Times New Roman", face="bold", size=16)) + #Times New Roman, 12pt, Bold
  labs(colour = "Group", x= "CSF amyloid", y= "Total outlier score") + # change label text
  scale_color_manual(values=c("Controls" =  "grey65" ,  "MCI" ="mediumturquoise", "AD"="lightslateblue"))
```

# total_outlier_score x PTAU
```{r}
# linear
ggplot(z_csf, aes(x = PTAU , y = total_outlier_score, color= diagnosis.x )) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x , size = 1)

# quadratic
ggplot(z_csf, aes(x = PTAU, y = total_outlier_score )) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x + I(x^2), size = 1)

# lines for each group
p <- z_csf %>% ggplot(aes(PTAU, total_outlier_score)) 
p + 
  geom_point(aes(col = diagnosis.x)) + 
    geom_smooth(aes(col = diagnosis.x), method = 'lm') +
    theme(legend.background = element_rect(fill = "transparent"),
          legend.justification = c(0, 1),
          legend.position = c(0, 1))


# lines for each group
p <- z_csf %>% ggplot(aes(PTAU, total_outlier_score)) 
p + 
  geom_smooth(aes(col = diagnosis.x), method = 'lm', formula = y ~ x, fill= "snow2") +
  theme_minimal() +
  theme(text=element_text(family="Times New Roman", face="bold", size=16)) + #Times New Roman, 12pt, Bold
  labs(colour = "Group", x= "CSF phospho-tau ", y= "Total outlier score") + # change label text
  scale_color_manual(values=c("Controls" =  "grey65" ,  "MCI" ="mediumturquoise", "AD"="lightslateblue"))
```

# variables together 
```{r}
# PTAU and ABETA
  ggplot(z_csf, aes(x = PTAU , y = ABETA, color= diagnosis.x )) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x , size = 1)

# MEM and EF
  ggplot(z_cc, aes(x = ADNI_EF , y = ADNI_MEM, color= diagnosis.x )) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x , size = 1)
```
#-----------------------------------------------
# Linear regression on MMSE measures
#-----------------------------------------------
# Decriptives
```{r paged.print=FALSE}
describeBy(z_mmse$MMSCORE, z_mmse$diagnosis.x, IQR = T)
```

# Total MMSE score
```{r}
#unadjusted
summary(lm(MMSCORE ~ total_outlier_score, data = z_mmse))

#adjusted
summary(lm(MMSCORE ~ total_outlier_score + age.x + gender.x, data = z_mmse)) 

#adjusted ##interaction
summary(lm(MMSCORE ~ total_outlier_score*diagnosis.x + age.x + gender.x, data = z_mmse)) 

```

## Seperated by group
```{r}
#controls 
summary(lm(MMSCORE ~ total_outlier_score, data = z_mmse_controls)) 

#mci 
summary(lm(MMSCORE ~ total_outlier_score, data = z_mmse_mci)) 

#dementia
summary(lm(MMSCORE ~ total_outlier_score, data = z_mmse_dementia)) 
```
#-----------------------------------------------
# Visualisations
#-----------------------------------------------
# total_outlier_score x total MMSE score
```{r}

# linear
ggplot(z_mmse, aes(x = total_outlier_score , y = MMSCORE )) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x , size = 1)


# quadratic
ggplot(z_mmse, aes(x = total_outlier_score, y = MMSCORE, color= diagnosis.x)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x + I(x^2), size = 1)


# lines for each group

p <- z_mmse %>% ggplot(aes(total_outlier_score, MMSCORE)) 

p + 
  geom_point(aes(col = diagnosis.x)) + 
    geom_smooth(aes(col = diagnosis.x), method = 'lm', formula = y ~ x + I(x^2)) +
    theme(legend.background = element_rect(fill = "transparent"),
          legend.justification = c(0, 1),
          legend.position = c(0, 1))


```
# L_S_postcentral (primary motor cortex) x MMSE
```{r}
#Raw z-scores 

summary(lm(MMSCORE ~ L_S_postcentral*diagnosis.x + age.x + gender.x, data = z_mmse))

ggplot(z_mmse, aes(x = L_S_postcentral , y = MMSCORE, color= diagnosis.x)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", formula = y ~ x , size = 1)


# line though groups

z_mmse$diagnosis.x <- as.factor(z_mmse$diagnosis.x)
is.factor(z_mmse$diagnosis.x)

p <- z_mmse %>% ggplot(aes(L_S_postcentral, MMSCORE)) 

p + 
  geom_point(aes(col = diagnosis.x)) + 
    geom_smooth(aes(col = diagnosis.x), method = 'lm') +
    theme(legend.background = element_rect(fill = "transparent"),
          legend.justification = c(0, 1),
          legend.position = c(0, 1))

```


#-----------------------------------------------
# Statistics on APOE measures
#-----------------------------------------------
# apoe descriptive statistics total_outlier score
```{r paged.print=FALSE}
describeBy(z_apoe$total_outlier_score, z_apoe$apoe_status, IQR = T)
table(z_apoe$apoe_status, z_apoe$diagnosis)
```
# APOE Statistics
```{r paged.print=FALSE}
#table(z_apoe$total_outlier_score, z_apoe$apoe_status)
summary(lm(total_outlier_score ~ apoe_status*diagnosis, data = z_apoe))

TukeyHSD(aov(total_outlier_score ~ apoe_status*diagnosis, data = z_apoe))

```
# APOE Visualistaions
```{r}
ggplot(z_apoe, aes(y=total_outlier_score, x=apoe_status)) +
  geom_boxplot(varwidth = T, outlier.shape = 1, fill = "lightgrey", color = "midnightblue", outlier.color = "midnightblue")+
  theme_cowplot()
```
