---
title: "ADNI FS data stats"
output: html_notebook
---

#----------------------------------------------
# CODE SETUP
#----------------------------------------------
# Librarys
```{r setup}
library(dplyr)
library(psych)
library(tidyr)
library(readr)
library(stringr)
library(matrixStats)
library(ggseg)
library(ggsegExtra)
library(ggsegDesterieux)
library(cowplot)
library(data.table)
library(e1071)
library(ggplot2)
library(plot.matrix)
library(proxy)
library(RPMG)
library(ggseg)
```

# Clear workspace
```{r}
rm(list = ls())
```

#Read in data from ADNI_database
```{r}

df <- read.csv("~/OneDrive - University College London/Chapter 2 cross sectional AD/ADNI_project/Full_study/Input_NM/All_sites/ThickAvg_ADNI_crosssectional_final.csv")


#head(df)
#str(df)
```



#Reformat categorical variables to factors

```{r}
df$diagnosis <- as.factor(df$diagnosis)
df$diagnosis <- gsub("0", "Controls", df$diagnosis)
df$diagnosis <- gsub("5", "MCI", df$diagnosis)
df$diagnosis <- gsub("4", "Dementia", df$diagnosis)

df$site_id <- as.factor(df$site_id)

## 0= females 1= males
df$gender <- gsub("0", "Females", df$gender)
df$gender <- gsub("1", "Males", df$gender)
df$gender <- factor(df$gender)


```
#----------------------------------------------
# Demographic data
#----------------------------------------------
# How many n in group and how many males and females
```{r}
table(df$diagnosis)
table(df$gender)
```
#Descriptive stats

```{r paged.print=FALSE}
describeBy(df$Mean_Thickness, df$diagnosis)
d<-(describeBy(df$Mean_Thickness, df$diagnosis))

describeBy(df$age, df$diagnosis)

mean(df$age)
sd(df$age)

tapply(df$gender, df$diagnosis, summary)


```
#----------------------------------------------
# Mean Thickness stats
#----------------------------------------------
#LM
```{r}
summary(lm(Mean_Thickness ~ diagnosis, data = df))
s_2<- lm(Mean_Thickness ~ diagnosis, data = df)
confint(s_2)
```
```{r}
TukeyHSD(aov(Mean_Thickness ~ diagnosis, data = df))
```
# LM with age and sex covariates 
```{r}
summary(lm(Mean_Thickness ~ diagnosis + age + gender, data = df))
s_1<-lm(Mean_Thickness ~ diagnosis + age + gender, data = df)
confint(s_1)

anova(lm(Mean_Thickness ~ diagnosis + age + gender, data = df))

```
```{r}
TukeyHSD(aov(Mean_Thickness ~ diagnosis, data = df))
## can you do post hoc adjustments for covariates??

```
#----------------------------------------------
#Regional anaylsis 
#----------------------------------------------
# Across group comparions 
# - - - - - - - - - - - - - - - - - - - - - - - - 
#Apply ANOVA over all ROIs and save as data.frame
```{r paged.print=FALSE}

df.rois <- df %>% rename_at(vars((6:153)), ~ paste0(., '_rois'))

df.stats <- as.data.frame(sapply(X = df.rois[,grep("_rois", names(df.rois),value = T)], FUN = function(x) summary(aov(x ~ df.rois$diagnosis))[[1]][["Pr(>F)"]][1]))
names(df.stats) <- "p_value"
setDT(df.stats, keep.rownames = "ROI")
head(df.stats, 20)

```

#FDR correction
```{r}
df.stats <- cbind(df.stats, p.adjust(df.stats$p_value), method = "fdr")
names(df.stats)[3] <- "FDR.pvalue"
head(df.stats)

#!!!!! how many are significant 
```

#Apply ANOVA over all ROIs and save f_stats as data.frame
```{r}
df.f_stats <- as.data.frame(sapply(X = df.rois[,grep("_rois", names(df.rois),value = T)], FUN = function(x) summary(aov(x ~ df.rois$diagnosis))[[1]][["F value"]][1]))
names(df.f_stats) <- "f_stat"
setDT(df.f_stats, keep.rownames = "ROI")
head(df.f_stats, 20)

```

#ROIs that are significant after FDR correction. There are `r length(which(df.stats$FDR.pvalue <0.05))` corrected ROIs that remain significant.
```{r paged.print=FALSE}
df.stats[which(df.stats$FDR.pvalue <0.05),]

#df_to_edit <- df.stats[which(df.stats$FDR.pvalue <0.05),]

#write.csv(df_to_edit,'sig_rois_fdr.csv')

```


#Convert existing data to desterieux atlas format
```{r}

df.stats$ROI <- as.data.frame(gsub("_rois", "", df.stats$ROI))

left.df.stats <- df.stats %>%
  filter(str_detect(ROI, "L_"))
x <- gsub("L_", "", left.df.stats$ROI)
y <- gsub("G.S_", "G and S ", x)
z <- gsub("G_", "G ", y)
z1 <- gsub("S_", "S ", z)
z2 <- gsub("_", " ", z1)
z3 <- gsub(" bin", "", z2)
z4 <- gsub("\\.", " ", z3)
z5 <- gsub("cingul ", "cingul-", z4)
z6 <- gsub("Mid ", "Mid-", z5)
z7 <- gsub("Post ", "Post-", z6)
z8 <- gsub("inf ", "inf-", z7)
z9 <- gsub("med ", "med-", z8)
z10 <- gsub("sup ", "sup-", z9)
z11 <- gsub("Fis ant ", "Fis-ant-", z10)
z12 <- gsub("precentral ", "precentral-", z11)
z13 <- gsub("Fis pos ", "Fis-pos-", z12)
z14 <- gsub("lg S", "lg and S", z13)
z15 <- gsub("oc temp", "oc-temp", z14)
z16 <- gsub("sup and transversal", "sup-transversal", z15)
z17 <- gsub("orbital H Shaped", "orbital-H Shaped", z16)
z18 <- gsub("oc sup-transversal", "oc sup and transversal", z17)
z19 <- gsub("prim Jensen", "prim-Jensen", z18)
z20 <- gsub("S oc-temp med-Lingual", "S oc-temp med and Lingual", z19)
z21 <- gsub("lat fusifor", "lat-fusifor", z20)
z22 <- gsub("middle Lunatus", "middle and Lunatus", z21)
z23 <- gsub("intrapariet P trans", "intrapariet and P trans", z22)
renamed_ROIs <- gsub("Lat Fis post", "Lat Fis-post", z23)

desterieux_ROIs <- as.data.frame(desterieux %>% filter(hemi == "left"))$region
compare_lists <- cbind(sort(renamed_ROIs), sort(unique(desterieux_ROIs)))
list_matches <- compare_lists[,1] %in% compare_lists[,2]
compare_lists[!list_matches,]
## if no mismatches, than add to data.frame as region
left.df.stats$region <- renamed_ROIs


###right hemi

right.df.stats <- df.stats %>%
  filter(str_detect(ROI, "R_"))
x <- gsub("R_", "", right.df.stats$ROI)
y <- gsub("G.S_", "G and S ", x)
z <- gsub("G_", "G ", y)
z1 <- gsub("S_", "S ", z)
z2 <- gsub("_", " ", z1)
z3 <- gsub(" bin", "", z2)
z4 <- gsub("\\.", " ", z3)
z5 <- gsub("cingul ", "cingul-", z4)
z6 <- gsub("Mid ", "Mid-", z5)
z7 <- gsub("Post ", "Post-", z6)
z8 <- gsub("inf ", "inf-", z7)
z9 <- gsub("med ", "med-", z8)
z10 <- gsub("sup ", "sup-", z9)
z11 <- gsub("Fis ant ", "Fis-ant-", z10)
z12 <- gsub("precentral ", "precentral-", z11)
z13 <- gsub("Fis pos ", "Fis-pos-", z12)
z14 <- gsub("lg S", "lg and S", z13)
z15 <- gsub("oc temp", "oc-temp", z14)
z16 <- gsub("sup and transversal", "sup-transversal", z15)
z17 <- gsub("orbital H Shaped", "orbital-H Shaped", z16)
z18 <- gsub("oc sup-transversal", "oc sup and transversal", z17)
z19 <- gsub("prim Jensen", "prim-Jensen", z18)
z20 <- gsub("S oc-temp med-Lingual", "S oc-temp med and Lingual", z19)
z21 <- gsub("lat fusifor", "lat-fusifor", z20)
z22 <- gsub("middle Lunatus", "middle and Lunatus", z21)
z23 <- gsub("intrapariet P trans", "intrapariet and P trans", z22)
renamed_ROIs <- gsub("Lat Fis post", "Lat Fis-post", z23)

desterieux_ROIs <- as.data.frame(desterieux %>% filter(hemi == "right"))$region
compare_lists <- cbind(sort(renamed_ROIs), sort(unique(desterieux_ROIs)))
list_matches <- compare_lists[,1] %in% compare_lists[,2]
compare_lists[!list_matches,]


## if no mismatches, than add to data.frame as region
right.df.stats$region <- renamed_ROIs


```
# Plot FDR-correct p-values (0-0.06) using ggseg
```{r message=FALSE}

#left                               
left_pvalues <- ggseg(.data=left.df.stats, atlas = desterieux, mapping=aes(fill=FDR.pvalue), hemisphere = "left", colour = "white", size = 0.2) + 
scale_fill_gradientn(limits = c(0,0.05), colours =  rainbow.colors(5))

#right
right_pvalues <- ggseg(.data=right.df.stats, atlas = desterieux, mapping=aes(fill=FDR.pvalue), hemisphere = "right", colour = "white", size = 0.2) +
  scale_fill_gradientn(limits = c(0,0.05), colours = rainbow.colors(5))

plot_grid(left_pvalues,right_pvalues, nrow = 2, labels = "AUTO")

ggsave("~/Downloads/corticalthicknesspvalue_maps.pdf")

```
# - - - - - - - - - - - - - - - - - - - - - - - - 
# Pairwise comparions 
# - - - - - - - - - - - - - - - - - - - - - - - -
# Data prepration
```{r}
df.CD <- df[grep("Controls|Dementia", df$diagnosis), ] #Subset just Controls and Dementia ("CD")
df.CM <- df[grep("Controls|MCI", df$diagnosis), ] #Subset just Controls and MCI ("CM")
df.MD <- df[grep("MCI|Dementia", df$diagnosis), ] #Subset just MCI and Dementia ("MD")
```

# 1. Controls vs Dementia t-test
```{r}
df.CD_stats <- as.data.frame(sapply(df.CD[6:153], function(x) t.test(x ~ df.CD$diagnosis)$statistic))
df.CD_stats1 <- as.data.frame(sapply(df.CD[6:153], function(x) t.test(x ~ df.CD$diagnosis)$p.value))
df.CD_stats2 <- as.data.frame(sapply(df.CD[6:153], function(x) t.test(x ~ df.CD$diagnosis)$parameter))
##? other measures?
df.CD_stats <- cbind(df.CD_stats ,df.CD_stats1)
df.CD_stats <- cbind(df.CD_stats ,df.CD_stats2)
rm(df.CD_stats1,df.CD_stats2)
``` 
# Column clean up
```{r}
df.CD_stats$t_statistic <- df.CD_stats[2] #rename col
names(df.CD_stats) <- c('statistic', 'p.value', 'parameter')
df.CD_stats[4] <- NULL
``` 
# FDR correction 
```{r}
df.CD_stats <- cbind(df.CD_stats, p.adjust(df.CD_stats$p.value), method = "fdr")
names(df.CD_stats)[4] <- "FDR.pvalue"
df.CD_stats[5] <- NULL
```
# Column clean up
```{r}
df.CD_stats <- tibble::rownames_to_column(df.CD_stats, "ROI") #Create ROI col
df.CD_stats$ROI <- gsub(".t", "", df.CD_stats$ROI) #clean up ROI names
```
# ROIs significant post FDR correction
There are `r length(which(df.stats$FDR.pvalue <0.05))` corrected ROIs that remain significant.
```{r paged.print=FALSE}
#df.CD_stats[which(df.CD_stats$FDR.pvalue <0.05),] 
df.CD_stats_sig <- df.CD_stats[which(df.CD_stats$FDR.pvalue <0.05),]
write.csv(df.CD_stats_sig,'CD_sig_rois_fdr.csv')
```
#Convert to desterieux atlas format
```{r}
df.CD_stats$ROI <- as.data.frame(gsub("_rois", "", df.CD_stats$ROI))

left.df.CD_stats <- df.CD_stats %>%
  filter(str_detect(ROI, "L_"))
x <- gsub("L_", "", left.df.CD_stats$ROI)
y <- gsub("G.S_", "G and S ", x)
z <- gsub("G_", "G ", y)
z1 <- gsub("S_", "S ", z)
z2 <- gsub("_", " ", z1)
z3 <- gsub(" bin", "", z2)
z4 <- gsub("\\.", " ", z3)
z5 <- gsub("cingul ", "cingul-", z4)
z6 <- gsub("Mid ", "Mid-", z5)
z7 <- gsub("Post ", "Post-", z6)
z8 <- gsub("inf ", "inf-", z7)
z9 <- gsub("med ", "med-", z8)
z10 <- gsub("sup ", "sup-", z9)
z11 <- gsub("Fis ant ", "Fis-ant-", z10)
z12 <- gsub("precentral ", "precentral-", z11)
z13 <- gsub("Fis pos ", "Fis-pos-", z12)
z14 <- gsub("lg S", "lg and S", z13)
z15 <- gsub("oc temp", "oc-temp", z14)
z16 <- gsub("sup and transversal", "sup-transversal", z15)
z17 <- gsub("orbital H Shaped", "orbital-H Shaped", z16)
z18 <- gsub("oc sup-transversal", "oc sup and transversal", z17)
z19 <- gsub("prim Jensen", "prim-Jensen", z18)
z20 <- gsub("S oc-temp med-Lingual", "S oc-temp med and Lingual", z19)
z21 <- gsub("lat fusifor", "lat-fusifor", z20)
z22 <- gsub("middle Lunatus", "middle and Lunatus", z21)
z23 <- gsub("intrapariet P trans", "intrapariet and P trans", z22)
renamed_ROIs <- gsub("Lat Fis post", "Lat Fis-post", z23)

desterieux_ROIs <- as.data.frame(desterieux %>% filter(hemi == "left"))$region
compare_lists <- cbind(sort(renamed_ROIs), sort(unique(desterieux_ROIs)))
list_matches <- compare_lists[,1] %in% compare_lists[,2]
compare_lists[!list_matches,]
## if no mismatches, than add to data.frame as region
left.df.CD_stats$region <- renamed_ROIs


###right hemi

right.df.CD_stats <- df.CD_stats %>%
  filter(str_detect(ROI, "R_"))
x <- gsub("R_", "", right.df.CD_stats$ROI)
y <- gsub("G.S_", "G and S ", x)
z <- gsub("G_", "G ", y)
z1 <- gsub("S_", "S ", z)
z2 <- gsub("_", " ", z1)
z3 <- gsub(" bin", "", z2)
z4 <- gsub("\\.", " ", z3)
z5 <- gsub("cingul ", "cingul-", z4)
z6 <- gsub("Mid ", "Mid-", z5)
z7 <- gsub("Post ", "Post-", z6)
z8 <- gsub("inf ", "inf-", z7)
z9 <- gsub("med ", "med-", z8)
z10 <- gsub("sup ", "sup-", z9)
z11 <- gsub("Fis ant ", "Fis-ant-", z10)
z12 <- gsub("precentral ", "precentral-", z11)
z13 <- gsub("Fis pos ", "Fis-pos-", z12)
z14 <- gsub("lg S", "lg and S", z13)
z15 <- gsub("oc temp", "oc-temp", z14)
z16 <- gsub("sup and transversal", "sup-transversal", z15)
z17 <- gsub("orbital H Shaped", "orbital-H Shaped", z16)
z18 <- gsub("oc sup-transversal", "oc sup and transversal", z17)
z19 <- gsub("prim Jensen", "prim-Jensen", z18)
z20 <- gsub("S oc-temp med-Lingual", "S oc-temp med and Lingual", z19)
z21 <- gsub("lat fusifor", "lat-fusifor", z20)
z22 <- gsub("middle Lunatus", "middle and Lunatus", z21)
z23 <- gsub("intrapariet P trans", "intrapariet and P trans", z22)
renamed_ROIs <- gsub("Lat Fis post", "Lat Fis-post", z23)

desterieux_ROIs <- as.data.frame(desterieux %>% filter(hemi == "right"))$region
compare_lists <- cbind(sort(renamed_ROIs), sort(unique(desterieux_ROIs)))
list_matches <- compare_lists[,1] %in% compare_lists[,2]
compare_lists[!list_matches,]


## if no mismatches, than add to data.frame as region
right.df.CD_stats$region <- renamed_ROIs

```
 Plot FDR-correct p-values (0-0.06) using ggseg
```{r message=FALSE}

#left                               
left_CD_pvalues <- ggseg(.data=left.df.CD_stats, atlas = desterieux, mapping=aes(fill=FDR.pvalue), hemisphere = "left", colour = "white", size = 0.2) + 
scale_fill_gradientn(limits = c(0,0.05), colours =  rainbow.colors(5))

#right
right_CD_pvalues <- ggseg(.data=right.df.CD_stats, atlas = desterieux, mapping=aes(fill=FDR.pvalue), hemisphere = "right", colour = "white", size = 0.2) +
  scale_fill_gradientn(limits = c(0,0.05), colours = rainbow.colors(5))

plot_grid(left_CD_pvalues,right_CD_pvalues, nrow = 2, labels = "AUTO")

ggsave("~/Downloads/corticalthicknesspvalue_maps.pdf")


```
#-
#-
# 2. Controls vs MCI t-test
```{r}
df.CM_stats <- as.data.frame(sapply(df.CM[6:153], function(x) t.test(x ~ df.CM$diagnosis)$statistic))
df.CM_stats1 <- as.data.frame(sapply(df.CM[6:153], function(x) t.test(x ~ df.CM$diagnosis)$p.value))
df.CM_stats2 <- as.data.frame(sapply(df.CM[6:153], function(x) t.test(x ~ df.CM$diagnosis)$parameter))
##? other measures?
df.CM_stats <- cbind(df.CM_stats ,df.CM_stats1)
df.CM_stats <- cbind(df.CM_stats ,df.CM_stats2)
rm(df.CM_stats1,df.CM_stats2)
``` 
# Column clean up
```{r}
df.CM_stats$t_statistic <- df.CM_stats[2] #rename col
names(df.CM_stats) <- c('statistic', 'p.value', 'parameter')
df.CM_stats[4] <- NULL
``` 
# FDR correction 
```{r}
df.CM_stats <- cbind(df.CM_stats, p.adjust(df.CM_stats$p.value), method = "fdr")
names(df.CM_stats)[4] <- "FDR.pvalue"
df.CM_stats[5] <- NULL
```
# Column clean up
```{r}
df.CM_stats <- tibble::rownames_to_column(df.CM_stats, "ROI") #Create ROI col
df.CM_stats$ROI <- gsub(".t", "", df.CM_stats$ROI) #clean up ROI names
```
# ROIs significant post FDR correction
There are `r length(which(df.stats$FDR.pvalue <0.05))` corrected ROIs that remain significant.
```{r paged.print=FALSE}
#df.CM_stats[which(df.CM_stats$FDR.pvalue <0.05),] 
df.CM_stats_sig <- df.CM_stats[which(df.CM_stats$FDR.pvalue <0.05),]
write.csv(df.CM_stats_sig,'CM_sig_rois_fdr.csv')
```
# 3. MCI vs Dementia t-test
```{r}
df.MD_stats <- as.data.frame(sapply(df.MD[6:153], function(x) t.test(x ~ df.MD$diagnosis)$statistic))
df.MD_stats1 <- as.data.frame(sapply(df.MD[6:153], function(x) t.test(x ~ df.MD$diagnosis)$p.value))
df.MD_stats2 <- as.data.frame(sapply(df.MD[6:153], function(x) t.test(x ~ df.MD$diagnosis)$parameter))
##? other measures?
df.MD_stats <- cbind(df.MD_stats ,df.MD_stats1)
df.MD_stats <- cbind(df.MD_stats ,df.MD_stats2)
rm(df.MD_stats1,df.MD_stats2)
``` 
# Column clean up
```{r}
df.MD_stats$t_statistic <- df.MD_stats[2] #rename col
names(df.MD_stats) <- c('statistic', 'p.value', 'parameter')
df.MD_stats[4] <- NULL
``` 
# FDR correction 
```{r}
df.MD_stats <- cbind(df.MD_stats, p.adjust(df.MD_stats$p.value), method = "fdr")
names(df.MD_stats)[4] <- "FDR.pvalue"
df.MD_stats[5] <- NULL
```
# Column clean up
```{r}
df.MD_stats <- tibble::rownames_to_column(df.MD_stats, "ROI") #Create ROI col
df.MD_stats$ROI <- gsub(".t", "", df.MD_stats$ROI) #clean up ROI names
```
# ROIs significant post FDR correction
There are `r length(which(df.stats$FDR.pvalue <0.05))` corrected ROIs that remain significant.
```{r paged.print=FALSE}
#df.MD_stats[which(df.MD_stats$FDR.pvalue <0.05),]
df.MD_stats_sig <- df.MD_stats[which(df.MD_stats$FDR.pvalue <0.05),]
write.csv(df.MD_stats_sig,'MD_sig_rois_fdr.csv')
```
