---
title: "Diagnosis conversion statistics"
author: "Serena Verdi"
date: "02/12/2021"
output: html_document
---
Summary: This script runs cox regression on converters data and generates kaplan-meier plots for visualisation. Converters data will need to be inputed to have the following variables: (1) conversion time (time to convert) and (2) conversion type (MCI to AD or controls to MCI)

Note: 'Cleaning_additional_variables' will need to be run prior for additional variables included as covariates in the model.

Paths to data will need to be changed accordingly.
#-----------------------------------------------
# Code setup
#-----------------------------------------------
# Librarys
```{r setup}
library(dplyr)
library(psych)
library(tidyr)
library(readr)
library(ADNIMERGE)
library(data.table)
library(matrixStats)
library(lubridate)
library(survival)
library(survminer)
#library(ggpubr)
#library(car)
library(ggplot2)
library(stringr)
library(ggseg)
library(ggsegExtra)
library(ggsegDesterieux)
library(RPMG)
```

# Clear workspace
```{r}
rm(list = ls())
```
#Read in data 

```{r}
# conversion status
#converters <-  read.csv("~/OneDrive - University College London/Chapter 2 cross sectional AD/ADNI_project/Full_study/Converters/Controls_MCI_converters.csv")
converters <-  read.csv("~/OneDrive - University College London/Chapter 2 cross sectional AD/ADNI_project/Full_study/Converters/MCI_AD_converters.csv")

followup_presence <-  read.csv("~/OneDrive - University College London/Chapter 2 cross sectional AD/ADNI_project/Full_study/Converters/everyone_with_followup_in_survtime2.csv") #examdate

# z-score data
z_score <- read.csv("~/OneDrive - University College London/Chapter 2 cross sectional AD/ADNI_project/Full_study/Output_NM/Output_70split_all_sites/NM_output_70_site62_subjectids.csv") 


## Additional Variables 

# Composite Cognitive Score
z_cc <- read.csv("~/OneDrive - University College London/Chapter 2 cross sectional AD/ADNI_project/Full_study/Results/z_score_stats_cognition/z_scores_cc.csv")

# MMSE  
z_mmse <- read.csv("~/OneDrive - University College London/Chapter 2 cross sectional AD/ADNI_project/Full_study/Results/z_score_stats_cognition/z_score_mmse_updated.csv")  

# APOE status
z_apoe <- read.csv("~/OneDrive - University College London/Chapter 2 cross sectional AD/ADNI_project/Full_study/Results/z_score_biospec/z_scores_apoe.csv")
```
#-----------------------------------------------
#Create dataset for stats
#-----------------------------------------------
# Prepare data
```{r}
followup_presence <- followup_presence %>% dplyr::rename(conversiontime = sbd) 
followup_presence$conversiontype <- c("stable") 

converters <- filter(converters, conversiontime <= 3) ## timediffconv2 change here !!!

df <- rbind(followup_presence,converters) #bind together

df <- df[-grep("X",names(df))] # drop unwanted cols



df$conversiontype <- gsub("MCI_to_AD", "1", df$conversiontype)  # 1 event happened
df$conversiontype <- gsub("stable", "0", df$conversiontype)  # 0 censored

df <- df[order(df$conversiontype, decreasing = TRUE),]

df <- df %>%  distinct(RID, .keep_all = TRUE) # keep distinct (ordered)
table(df$conversiontype)
```
# Prepare data: recode
```{r}

df <- df %>% dplyr::rename(status = conversiontype) 

```

# Thresholding and binersing z-scores 
```{r}
# outlier_threshold <- -1.65 ## bottom 5%
outlier_threshold <- -1.96 ## bottom 2.5%
# outlier_threshold <- -2.58 ## bottom 0.05%

temp<- as.data.frame(ifelse(z_score[,6:154] < outlier_threshold,1,0))
temp <- temp %>% rename_all(paste0, "_bin")
z_score$total_outlier_score <- rowSums(temp)
z_score <- cbind(z_score, temp)
rm(temp)
```
# Thresholding and binersing total_outlier_score using median
```{r}
hist(z_score$total_outlier_score)
m <-  as.numeric(median(z_score$total_outlier_score))
total_outlier_threshold <- m ## low outlier score (lower than median)
#rm(m)

temp2 <- as.data.frame(ifelse(z_score[156] < total_outlier_threshold,2,1)) ## 1= high ; 2= low
temp2 <- temp2 %>% dplyr::rename(total_outlier_threshold = total_outlier_score) #rename cols
z_score <- cbind(z_score, temp2)
z_score <- z_score %>% relocate(total_outlier_threshold, .after = total_outlier_score) 
#rm(temp2)
hist(z_score$total_outlier_threshold)

```

# Merge z-scores and conversion status and censored status
```{r}
z_score <- z_score %>% dplyr::rename(RID = rid) # recode rid to RID
z_score <- merge(df, z_score, by= "RID", all.x = TRUE) #merge  


```

# Old code - ignore: Clean up z_score and censored status
```{r}
# z_score <- z_score[-grep("X",names(z_score))]  # remove unwanted cols
# 
# z_score[["conversion_status"]][is.na(z_score[["conversion_status"]])] <- 0 #recode missing values to 1 = censored  
# z_score$conversion_status <-  as.numeric(z_score$conversion_status)
# 
# 
# z_score[["conversiontime"]][is.na(z_score[["conversiontime"]])] <- 3  #recode missing time values to x years ## change here !!!
# z_score$conversiontime <-  as.numeric(z_score$conversiontime)
# 
# 
# z_score[["censored_status"]][is.na(z_score[["censored_status"]])] <- 1 #recode missing values to 1 = censored  
# z_score$censored_status <-  as.numeric(z_score$censored_status)
```

#Merge with Additional Variables
```{r}
z_cc <- z_cc[grep("RID|ADNI_MEM|ADNI_EF",names(z_cc))]  # remove unwanted cols
z_mmse <- z_mmse[grep("RID|MMSCORE",names(z_mmse))]  # remove unwanted cols
z_apoe <- z_apoe[grep("RID|apoe_status",names(z_apoe))]  # remove unwanted cols


z_score <- merge(z_score, z_cc, by= "RID", all.x = TRUE) #merge  
z_score <- merge(z_score, z_mmse, by= "RID", all.x = TRUE) #merge  
z_score <- merge(z_score, z_apoe, by= "RID", all.x = TRUE) #merge  
```

# Convert ids which are Diagnosis dementia back into MCI
```{r}
# filter dementia
temp <-  z_score %>% 
   filter(diagnosis %in% c("Dementia"))

temp$status <-  gsub("0", "1", temp$status)  # relabel as MCI converters (1)

temp$diagnosis <-  gsub("Dementia", "MCI", temp$diagnosis)  # relabel as MCI converters (1)


# bind 
z_score <- rbind(z_score,temp)


# remove dementia and control data

#z_score <-  z_score %>% 
   #filter(diagnosis %in% c("MCI"))

#as numeric

z_score$status <-  as.numeric(z_score$status)
z_score$conversiontime <-  as.numeric(z_score$conversiontime)
```


#-----------------------------------------------
#Stats
#-----------------------------------------------
#COX
## Cox regression - total outlier score
```{r}
# total_outlier_score as predictor
cox <- coxph(Surv(conversiontime, status) ~ total_outlier_score, data = z_score)
summary(cox)

# total_outlier_score and total MMSE score as predictor
cox1 <- coxph(Surv(conversiontime, status) ~ total_outlier_score + MMSCORE + age + gender + apoe_status, data = z_score)
summary(cox1)

```
## Cox interpretation - total outlier score
```{r}

# for every 10 points on the outlier score, there's a 30% increased risk of converting within 3 years

coef <- as.numeric (cox[1]) #what is the coef
outlier_increment <-  10 # define:total outlier score example increment

x <- coef*outlier_increment
risk <- exp(x)

risk <- risk -1 
risk <- risk*100
risk
```

## Plot Cox regression  - total outlier score
```{r}
plot(survfit(cox1), xscale = 1,
     xlab = "Years to convert",
     ylab = "Proportion of subjects")
```
```{r}
# total_outlier_score as predictor
#cox1 <- coxph(Surv(conversiontime, status) ~ L_G_oc.temp_med.Parahip, data = z_score)
#cox2 <- coxph(Surv(conversiontime, status) ~ L_G.S_cingul.Ant, data = z_score)
```


## Cox regression - each roi (incomplete- did not decide to do this as focus is not on the area/ antireductionalist)
```{r}

#test <- z_score[,-grep("_bin",names(z_score))]
#test <- test[,grep("R_|L_|conversiontime|status",names(test))]
#test <- t(test)

#f_cox <- function(varROI) {

  #cox <- coxph(Surv(conversiontime, status) ~ varROI, data = test)
  #cox.stats_output <- summary(cox)$coefficients
  #cox.stats <-  as.data.frame(cox.stats)[[5]]
  #return (cox.stats)
  
#}

#lapply(test[3:151], f_cox) 


# example function
#df.stats <- 
  #as.data.frame(sapply(X = df[,grep("_bin", names(df),value = T)], FUN = function(x) summary(aov(x ~ df$diagnosis))[[1]][["Pr(>F)"]][1]))


#test

#cox <- coxph(Surv(conversiontime, status) ~ test$L_G.S_cingul.Ant, data = test)
#cox.stats <- summary(cox)$coefficients
#cox.stats[, 5]

```

#KM PLOT
##Kaplan-Meier (split by median)

```{r}
f1 <- survfit(Surv(conversiontime, status) ~ total_outlier_threshold, data = z_score)

summary(f1)
```
##Kaplan-Meier plot
```{r}

plot(survfit(Surv(conversiontime, status) ~ total_outlier_threshold, data = z_score), 
     xlab = "Years", 
     ylab = "Overall conversion probability")
```
##Kaplan-Meier ggsurvplot
```{r}
ggsurvplot(
    fit = survfit(Surv(conversiontime, status) ~ total_outlier_threshold, data = z_score), 
  conf.int = T, 
    xlab = "Years", 
    ylab = "Proportional Conversion")
## 1= more outliers ; 2= less ouliers
```

```{r}
ggsurvplot(
  fit = survfit(Surv(conversiontime, status) ~ total_outlier_threshold, data = z_score),
  size = 1,                 # change line size
  palette =
    c("indianred2", "steelblue2"),# custom color palettes
  conf.int = TRUE,          # Add confidence interval
    xlab = "Years", 
    ylab = "Proportional Conversion",
  pval = FALSE,              # Add p-value
  risk.table = FALSE,        # Add risk table
  #risk.table.col = "strata",# Risk table color by groups
  legend.labs =
    c("High total outlier score", "Low total outlier score"),    # Change legend labels
  #risk.table.height = 0.25, # Useful to change when you have multiple groups
  ggtheme = theme_bw()      # Change ggplot2 theme
)


```
#-----------------------------------------------
#Outlier plots
#-----------------------------------------------


# Thresholding and binersing z-scores 
```{r}
temp<- as.data.frame(ifelse(z_score_1[,6:153] < outlier_threshold,1,0))
temp <- temp %>% rename_all(paste0, "_bin")
z_score_1$total_outlier_score <- rowSums(temp)
z_score_1 <- cbind(z_score_1, temp)
rm(temp)
```
# Merge z-scores and converters
```{r}
z_score_1 <- z_score_1 %>% dplyr::rename(RID = rid) # recode rid to RID
df_converters <- merge(converters, z_score_1, by= "RID", all.x = FALSE) #merge  
```
# Proportional maps
```{r}


df_converters_proportions <-as.data.frame(sapply(X = df_converters[,grep("_bin", names(df_converters),value = T)], FUN = function(x) sum(with(df_converters,x))))
colnames(df_converters_proportions)[1] <- "count"
df_converters_proportions$proportion <- df_converters_proportions$count/76
df_converters_proportions <- dplyr::as_tibble(df_converters_proportions, rownames = "ROI")

```
##Convert existing data to desterieux atlas
```{r}

left.df_converters_proportions <- df_converters_proportions %>%
  filter(str_detect(ROI, "L_"))
x <- gsub("L_", "", left.df_converters_proportions$ROI)
y <- gsub("G.S_", "G and S ", x)
z <- gsub("G_", "G ", y)
z1 <- gsub("S_", "S ", z)
z2 <- gsub("_", " ", z1)
z3 <- gsub(" bin", "", z2)
z4 <- gsub("\\.", " ", z3)
z5 <- gsub("cingul ", "cingul-", z4)
z6 <- gsub("Mid ", "Mid-", z5)
z7 <- gsub("Post ", "Post-", z6)
z8 <- gsub("inf ", "inf-", z7)
z9 <- gsub("med ", "med-", z8)
z10 <- gsub("sup ", "sup-", z9)
z11 <- gsub("Fis ant ", "Fis-ant-", z10)
z12 <- gsub("precentral ", "precentral-", z11)
z13 <- gsub("Fis pos ", "Fis-pos-", z12)
z14 <- gsub("lg S", "lg and S", z13)
z15 <- gsub("oc temp", "oc-temp", z14)
z16 <- gsub("sup and transversal", "sup-transversal", z15)
z17 <- gsub("orbital H Shaped", "orbital-H Shaped", z16)
z18 <- gsub("oc sup-transversal", "oc sup and transversal", z17)
z19 <- gsub("prim Jensen", "prim-Jensen", z18)
z20 <- gsub("S oc-temp med-Lingual", "S oc-temp med and Lingual", z19)
z21 <- gsub("lat fusifor", "lat-fusifor", z20)
z22 <- gsub("middle Lunatus", "middle and Lunatus", z21)
z23 <- gsub("intrapariet P trans", "intrapariet and P trans", z22)
renamed_ROIs <- gsub("Lat Fis post", "Lat Fis-post", z23)

desterieux_ROIs <- as.data.frame(desterieux %>% filter(hemi == "left"))$region
compare_lists <- cbind(sort(renamed_ROIs), sort(unique(desterieux_ROIs)))
list_matches <- compare_lists[,1] %in% compare_lists[,2]
compare_lists[!list_matches,]
## if no mismatches, than add to data.frame as region
left.df_converters_proportions$region <- renamed_ROIs

right.df_converters_proportions <- df_converters_proportions %>%
  filter(str_detect(ROI, "R_"))
x <- gsub("R_", "", right.df_converters_proportions$ROI)
y <- gsub("G.S_", "G and S ", x)
z <- gsub("G_", "G ", y)
z1 <- gsub("S_", "S ", z)
z2 <- gsub("_", " ", z1)
z3 <- gsub(" bin", "", z2)
z4 <- gsub("\\.", " ", z3)
z5 <- gsub("cingul ", "cingul-", z4)
z6 <- gsub("Mid ", "Mid-", z5)
z7 <- gsub("Post ", "Post-", z6)
z8 <- gsub("inf ", "inf-", z7)
z9 <- gsub("med ", "med-", z8)
z10 <- gsub("sup ", "sup-", z9)
z11 <- gsub("Fis ant ", "Fis-ant-", z10)
z12 <- gsub("precentral ", "precentral-", z11)
z13 <- gsub("Fis pos ", "Fis-pos-", z12)
z14 <- gsub("lg S", "lg and S", z13)
z15 <- gsub("oc temp", "oc-temp", z14)
z16 <- gsub("sup and transversal", "sup-transversal", z15)
z17 <- gsub("orbital H Shaped", "orbital-H Shaped", z16)
z18 <- gsub("oc sup-transversal", "oc sup and transversal", z17)
z19 <- gsub("prim Jensen", "prim-Jensen", z18)
z20 <- gsub("S oc-temp med-Lingual", "S oc-temp med and Lingual", z19)
z21 <- gsub("lat fusifor", "lat-fusifor", z20)
z22 <- gsub("middle Lunatus", "middle and Lunatus", z21)
z23 <- gsub("intrapariet P trans", "intrapariet and P trans", z22)
renamed_ROIs <- gsub("Lat Fis post", "Lat Fis-post", z23)

desterieux_ROIs <- as.data.frame(desterieux %>% filter(hemi == "right"))$region
compare_lists <- cbind(sort(renamed_ROIs), sort(unique(desterieux_ROIs)))
list_matches <- compare_lists[,1] %in% compare_lists[,2]
compare_lists[!list_matches,]

## if no mismatches, than add to data.frame as region
right.df_converters_proportions$region <- renamed_ROIs
```
## Plot outliers using ggseg !!!!! check limits
```{r message=FALSE}
                           
left <- ggseg(.data=left.df_converters_proportions, atlas = desterieux, mapping=aes(fill=proportion), hemisphere = "left", colour = "white", size = 0.2) + 
scale_fill_gradientn(limits = c(0.025,1), colours =  rev(rainbow.colors(5)))

right <- ggseg(.data=right.df_converters_proportions, atlas = desterieux, mapping=aes(fill=proportion), hemisphere = "right", colour = "white", size = 0.2) +
  scale_fill_gradientn(limits = c(0.025,1), colours = rev(rainbow.colors(5)))

plot_grid(left,right, nrow = 2, labels = "AUTO")
ggsave("~/OneDrive - University College London/Chapter 2 cross sectional AD/ADNI_project/Full_study/Results/converters_proportions.pdf") 
```
